## cleaning biodiversity data

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## Load libraries

```{r load}
library('scrubr')
```

We'll use sample datasets included with the package, they are lazy loaded,
and available via `sample_data_1` and `sample_data_2`

## Coordinate based cleaning

Remove impossible coordinates (using sample data included in the pkg)

```{r}
dframe(sample_data_1) %>% coord_impossible()
```

Remove incomplete coordinates

```{r}
dframe(sample_data_1) %>% coord_incomplete()
```

Remove unlikely coordinates (e.g., those at 0,0)

```{r}
dframe(sample_data_1) %>% coord_unlikely()
```

Do all three

```{r}
dframe(sample_data_1) %>%
  coord_impossible() %>%
  coord_incomplete() %>%
  coord_unlikely()
```

Don't drop bad data

```{r}
dframe(sample_data_1) %>% coord_incomplete(drop = TRUE) %>% NROW
dframe(sample_data_1) %>% coord_incomplete(drop = FALSE) %>% NROW
```

## Deduplicate

```{r}
smalldf <- sample_data_1[1:20, ]
# create a duplicate record
smalldf <- rbind(smalldf, smalldf[10,])
row.names(smalldf) <- NULL
# make it slightly different
smalldf[21, "key"] <- 1088954555
NROW(smalldf)
dp <- dframe(smalldf) %>% dedup()
NROW(dp)
attr(dp, "dups")
```

## Dates

Standardize/convert dates

```{r}
dframe(sample_data_1) %>% date_standardize("%d%b%Y")
```

Drop records without dates

```{r}
NROW(sample_data_1)
NROW(dframe(sample_data_1) %>% date_missing())
```

Create date field from other fields

```{r}
dframe(sample_data_2) %>% date_create(year, month, day)
```

## Taxonomy

Only one function - remove rows where taxonomic names are either missing an epithet, or are missing altogether  (`NA` or `NULL`).

Get some data from GBIF, via `rgbif`

```{r}
if (requireNamespace("rgbif", quietly = TRUE)) {
  library("rgbif")
  res <- occ_data(limit = 500)$data
} else {
  res <- sample_data_3
}
```

Clean names

```{r}
NROW(res)
df <- dframe(res) %>% tax_no_epithet(name = "name")
NROW(df)
attr(df, "name_var")
attr(df, "tax_no_epithet")
```
