### rgbif

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

### Load libraries

```{r}
library('rgbif')
```

## Number of occurrences

Search by type of record, all observational in this case

```{r occ_count1}
occ_count(basisOfRecord='OBSERVATION')
```

Records for **Puma concolor** with lat/long data (georeferened) only. Note that `hasCoordinate` in `occ_search()` is the same as `georeferenced` in `occ_count()`.

```{r occ_count2}
occ_count(taxonKey=2435099, georeferenced=TRUE)
```

Records from Denmark

```{r occ_count4}
denmark_code <- isocodes[grep("Denmark", isocodes$name), "code"]
occ_count(country=denmark_code)
```

## Search for taxon names

* `name_lookup()` does full text search of all name data.

```{r}
out <- name_lookup(query = 'mammalia')
```

```{r}
names(out)
```

```{r}
out$meta
```

```{r}
head(out$data)
```

```{r}
out$facets
```

```{r}
out$hierarchies[1:2]
```

```{r}
out$names[2]
```

* `name_backbone()` - search against the GBIF backbone taxonomy

```{r}
name_backbone(name = 'Helianthus', rank = 'genus', kingdom = 'plants')
```


## Single occurrence records

Get data for a single occurrence. Note that data is returned as a list, with slots for metadata and data, or as a hierarchy, or just data.

Just data

```{r occ_get1}
occ_get(key = 766766824, return = 'data')
```

Just taxonomic hierarchy

```{r occ_get2}
occ_get(key=766766824, return='hier')
```

Get many occurrences. `occ_get` is vectorized

```{r occ_get4}
occ_get(key=c(766766824, 101010, 240713150, 855998194), return='data')
```


## Search for occurrences

* `occ_search()`

```{r}
occ_search(scientificName = "Ursus americanus", limit = 20)
```

Ideally, search for names first, make sure you have the right name, then pass the GBIF key to the `occ_search()` function:

```{r}
key <- name_suggest(q='Helianthus annuus', rank='species')$key[1]
occ_search(taxonKey=key, limit=20)
```

Most parameters are vectorized, so you can pass in more than one value:

```{r}
splist <- c('Cyanocitta stelleri', 'Junco hyemalis', 'Aix sponsa')
keys <- sapply(splist, function(x) name_suggest(x)$key[1], USE.NAMES = FALSE)
occ_search(taxonKey = keys, limit = 5)
```
