### spocc

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```


```{r load}
library('spocc')
```

## spocc unifies access to biodiversity data across sources

### Data sources

* [GBIF](http://www.gbif.org/)
* [BISON](http://bison.usgs.ornl.gov/)
* [eBird](http://ebird.org/content/ebird/)
* [iNaturalist](http://www.inaturalist.org/)
* [Berkeley Ecoengine](https://ecoengine.berkeley.edu/)
* [AntWeb](http://www.antweb.org/)
* [VertNet](http://vertnet.org/)
* [iDigBio](https://www.idigbio.org/)

## Get data

```{r sources}
out <- occ(query = 'Accipiter striatus', from = 'gbif')
```

GBIF data w/ metadata

```{r}
out$gbif
```

empty

```{r}
out$ebird$data
```

metadata, your query parameters, time the call executed, etc.

```{r}
out$gbif$meta
```

just data

```{r}
out$gbif$data
```

## Data Form

```
response -- |
            | -- gbif --- |
                          | -- meta 
                          | -- data -- | 
                                       | -- Accipiter_striatus
                                       | -- Puma_concolor
            | -- ecoengine
            ... and so on for each data source

```

## Combine data

`occ2df()` pulls a few key columns

```{r manysources}
out <- occ(query = 'Accipiter striatus', from = c('gbif', 'ebird'))
occ2df(out)
```

* Combining data within source easy 
* Combining data across data sources messy, but can be done - ask me
