## identifiers

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  message = FALSE,
  warning = FALSE
)
```

Taxonomic identifiers are the currency you need to convert your names to in order to get any other taxonomic data.

Unfortunately, there is no one identifier for each taxon to rule them all - each database has their own identifier for the same taxon.

Here, get identifiers from 5 different sources for *Poa annua*. Then we can pass those ids to other functions that act on those ids without any other input

_p.s. this also demonstrates the interactive prompt, as you'll see_

```{r}
library('taxize')
```

## Get ids from many sources at once

```{r output.lines=1:15}
out <- get_ids(names = "Poa annua", db = c('ncbi', 'itis', 'col', 'tropicos'))
out
```

```{r}
out$col
```

## From single source, e.g,: ITIS

```{r}
get_tsn("Poa annua")
```

## Coerce a name or id to a taxon identifier class

```{r}
get_gbifid("Poa annua")
```

```{r}
as.gbifid("7576620")
```

## Many names

In this case get many identifiers for many names

```{r output.lines=1:15}
mynames <- c("Helianthus annuus", "Pinus contorta", "Collomia grandiflora")
out <- get_ids(names = mynames, db = c('ncbi','itis','col','tropicos'))
```

```{r}
out$tropicos
```

```{r}
class(out)
```

```{r}
class(out$col)
```



